---
title: <span style="color:#666666">Dynamic R Report from Linear Model</span>
author: <span style="color:#ff6600">Jordan Wheeler</span>
runtime: shiny
output: 
    html_document:
      theme: cosmo
---
```{r include = FALSE}
library(car)
library(ggplot2)
library(MASS)
library(DT)
library(data.table)
library(plotly)
library(googleVis)
library(shinythemes)
library(knitr)
library(shiny)

data = data.frame(diamonds)
head(data)

full_model = lm(price~., data = data)
summary(full_model)

best_model = stepAIC(full_model, direction = "both", trace = FALSE)
best_model_summary = summary(best_model)
best_model_coef = best_model_summary$coefficients
best_model_coef = as.data.frame(best_model_coef)

column_names = names(best_model$coefficients[2:length(best_model$coefficients)])
column_names = gsub("\\..*","", column_names)
column_names = gsub("\\^.*","", column_names)
column_names = unique(column_names)

data2 = data[,(colnames(data) %in% column_names)]

row_names = rownames(best_model_coef)
row_names = gsub("\\..*","", row_names)
row_names = gsub("\\^.*","", row_names)
best_model_coef = data.frame(variables = row_names, best_model_coef)
best_model_coef = best_model_coef[,1:2]

best_model_coef = data.table(best_model_coef)
DoTDF = best_model_coef[, .(Estimate = sum(Estimate)), by = list(variables)]
best_model_coef = data.frame(DoTDF)

factor_vars = names(grep("factor", sapply(data2, class), value=TRUE))
best_model_coef[which(best_model_coef$variables %in% factor_vars),]$Estimate = best_model_coef[which(best_model_coef$variables %in% factor_vars),]$Estimate + best_model_coef[1,]$Estimate
best_model_coef = best_model_coef[-c(1),]

numdata = data2[sapply(data2, is.numeric)] 
column_means = colMeans(numdata)
column_means = as.data.frame(column_means)
row_names2 = rownames(column_means)
column_means = data.frame(variables = row_names2, column_means)
column_means

factor_vars_df = best_model_coef[which(best_model_coef$variables %in% factor_vars),]
factor_vars_df$column_means = 1

numeric_vars_df = merge(x = best_model_coef, y = column_means, by = "variables")
best_model_coef = rbind(factor_vars_df, numeric_vars_df)

best_model_coef$contributions = best_model_coef$Estimate * best_model_coef$column_means
best_model_coef$contribution_percent = abs(best_model_coef$contributions)/sum(abs(best_model_coef$contributions))

best_model_coef = best_model_coef[order(best_model_coef$contribution_percent, decreasing = TRUE),]

graph_text = paste("Variable: ", best_model_coef$variables, "\n", "Contribution: ", scales::percent(best_model_coef$contribution_percent))
```

## Automated Reports {style="color:#666666"}

Select a tab to see the specified report.

## {.tabset}
### Model Variables

<h4 style="text-align:center">Summary of Significant Variables:</h4> 
<h5 style="text-align:center">Connected to a database and created a model to determine the Price of a diamond based upon diamond attributes.</h5> 
<h5 style="text-align:center">Here is the result of the best model</h5>
<hr style="border-color: #ff6600;">

```{r echo = FALSE, warning = FALSE, fig.align = 'center'}
kable(as.data.frame(best_model_summary$coefficients))
```

### Model Statistics

<h4 style="text-align:center">Summary of Model:</h4> 
<h5 style="text-align:center">Statistical Results of the Model</h5> 
<hr style="border-color: #ff6600;">

<div align="center">
```{r echo = FALSE, warning = FALSE, fig.align = 'center'}
tags$h3("R-squared Value:", tags$b(textOutput("r_sq")))
tags$h3("Adjusted R-squared Value:", tags$b(textOutput("adj_r_sq")))
tags$h3("Degrees of Freedom:", tags$b(textOutput("deg_free")))
tags$h3("F-Statistic:", tags$b(textOutput("f_stat")))
tags$h3("Model (without coefficients):", tags$b(textOutput("model_call")))

output$r_sq = function() { paste(best_model_summary$r.squared) }
output$adj_r_sq = function() { paste(best_model_summary$adj.r.squared) }
output$deg_free = function() { paste(best_model_summary$df[2]) }
output$f_stat = function() { paste(best_model_summary$fstatistic[1]) }
output$model_call = function() { paste(best_model_summary$call) }
```
</div>
<br>
<br>

### Contributions by Variables

<h4 style="text-align:center">Contributions by Significant Variables:</h4>
<h5 style="text-align:center">Here is a graph of all the variables that contribute to the best model</h5>
<hr style="border-color: #ff6600;">
<br>
<br>

```{r echo = FALSE, warning = FALSE, fig.align = 'center'}
contribution_graph = ggplot(mapping = aes(x = reorder(best_model_coef$variables, -best_model_coef$contribution_percent), y = best_model_coef$contribution_percent)) +
  geom_bar(stat="identity", color = "white", fill = "steelblue") +
  geom_text(aes(label=scales::percent(best_model_coef$contribution_percent)), vjust=-.5, color="#666666") +
  scale_x_discrete("Variable") + 
  scale_y_continuous("Total Contribution", limits = c(0, (max(best_model_coef$contribution_percent)+.1)), expand = c(0,0)) + 
  ggtitle("Contribution of Variables") +
  theme_minimal() +
  theme(plot.title = element_text(color="#666666", face="bold", size=24)) +
  theme(axis.title = element_text(color="#666666", face="bold", size=16, margin= margin(t=1, r=1, b=1, l=1))) +
  theme(axis.text = element_text(color="#666666", size=10)) +
  theme(plot.title = element_text(hjust = .5)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
contribution_graph

```

### Independent Variable Relationship

<h4 style="text-align:center">Independent Variables vs. Target Variable:</h4> 
<h5 style="text-align:center">Here is a graph of a linear model that shows the relationship between the target variable and the selected variable. This will show you how the selected variable influences the target variable.</h5>
<hr style="border-color: #ff6600;">

<div align="center">
```{r echo = FALSE, warning = FALSE, fig.align = 'center', fig.width= 10}
inputPanel(
  selectInput("IndVar", "Select Independent Variable:",
              choices = sub("_", " ", best_model_coef$variables)))
renderPlotly({
  IndependentVar = sub(" ", "_", input$IndVar)
  print( 
  ggplotly(ggplotly(ggplot(data, aes(x = data[,IndependentVar], y = price)) + 
        geom_point() +
        stat_smooth(method = "lm", col = "blue") +
        ggtitle("Independent Variable vs.Target Variable\n") +
        labs(x = sub("_", " ", IndependentVar), y = "Price") +
        theme_minimal() +
        theme(plot.title = element_text(color="#666666", face="bold", size=24)) +
        theme(axis.title = element_text(color="#666666", face="bold", size=16, margin= margin(t=1, r=1, b=1, l=1))) +
        theme(axis.text = element_text(color="#666666", size=12)) +
        theme(plot.title = element_text(hjust = .5)))))
})
```
</div>

### Variable Breakdown

<h4 style="text-align:center">Variable Breakdown:</h4> 
<h5 style="text-align:center">Select a variable to see a box-plot that will show you specifics of that variable.</h5>
<hr style="border-color: #ff6600;">

<div align="center">
```{r echo = FALSE, warning = FALSE, fig.align = 'center', fig.width= 10}
inputPanel(
  selectInput("IndVar2", "Select Independent Variable:",
              choices = sub("_", " ", best_model_coef$variables)))

renderPlotly(plot_ly(y = data2[,sub(" ", "_", input$IndVar2)],
                     name = input$IndVar2,
                     type = "box") %>%
               layout(height = 750)
               )


  
```
</div>

### View Data

<h4 style="text-align:center">View Data Table:</h4> 
<hr style="border-color: #ff6600;">

<div align="center">
```{r echo = FALSE, warning = FALSE, fig.align = 'center'}
library(kableExtra)

inputPanel(
  fluidRow(tags$h4("Min Row:", textOutput("min_row")),textInput("start", "Start Row Number:", "1")),
  fluidRow("", column(12, style = "margin-top: 85px;", downloadButton("DLdata", "Download Current Table"))),
  fluidRow(tags$h4("Max Row:", textOutput("max_row")), textInput("end", "End Row Number:", "5"))
)

output$max_row = function() { paste(nrow(data)) }
output$min_row = function() { paste(nrow(data)-(nrow(data)-1)) }

htmlOutput("tabl")
output$tabl = renderGvis({
  h = ((as.numeric(input$end) - as.numeric(input$start)) + 2) * 30
  if (h > 500){
    h = paste(500, "px", sep = "")
  }
  else{
    h = paste(h, "px", sep = "")
  }
  gvisTable(data[as.numeric(input$start):as.numeric(input[["end"]]),], options = list(page = "enable", pageSize = 25))
})

output$DLdata = downloadHandler(
    filename = function() {
      paste("DataSet", ".csv", sep = "")
    },
    content = function(file) {
      write.csv((data[as.numeric(input$start):as.numeric(input[["end"]]),]), file, row.names = FALSE)
    }
  )
```
</div>

### Search Table

<h4 style="text-align:center">Search for an Entry:</h4> 
<hr style="border-color: #ff6600;">

<div align="center">
```{r echo = FALSE, warning = FALSE, fig.align = 'center'}

tags$div(style = "width: 90%;",
inputPanel(
  fluidRow(column(12, style = "margin-top: 5px;",
              selectInput("searchVar", "Select Independent Variable to Search By:",
              choices = best_model_coef$variables)),
           downloadButton("DLdata2", "Download Current Table")),
  fluidRow(tags$h4("Variable Range:"), tags$h5(textOutput("variable_range")),
           column(12, style = "margin-top: 5px;",
           textInput("searchVal", "Enter a Value to Filter:", "4"))),
  tags$div(align = "left",
           radioButtons("radio", label = h3("Choose Filter:"),
              choices = list("Less Than or Equal" = 1, "Equal" = 2, "Greater Than or Equal" = 3), 
              selected = 2)),
  fluidRow(tags$hr(), tags$div(align = "center", tags$h3("Number of Rows Slected:"), tags$hr(), tags$h4(tags$b(textOutput("numrows"))))))
)
  
  output$variable_range = function(){
    paste(min(data[,input$searchVar]), "-", max(data[,input$searchVar]))
  }

htmlOutput("tabl2")
output$tabl2 = renderGvis({
    if (input$radio == 1){
      gvisTable(data[data[,input$searchVar] <= as.numeric(input$searchVal),], options = list(page = "enable", pageSize = 25))
    }
    else if (input$radio == 2){
      gvisTable(data[data[,input$searchVar] == as.numeric(input$searchVal),], options = list(page = "enable", pageSize = 25))
    }
    else if (input$radio == 3){
      gvisTable(data[data[,input$searchVar] >= as.numeric(input$searchVal),], options = list(page = "enable", pageSize = 25))
    }
})
  
output$DLdata2 = downloadHandler(
    filename = function() {
      paste("DataSet", ".csv", sep = "")
    },
    content = function(file) {
      write.csv({if (input$radio == 1){data[data[,input$searchVar] <= as.numeric(input$searchVal),]}
    else if (input$radio == 2){data[data[,input$searchVar] == as.numeric(input$searchVal),]}
    else if (input$radio == 3){data[data[,input$searchVar] >= as.numeric(input$searchVal),]}}, file, row.names = FALSE)
    }
  )

output$numrows = function() {
    if (input$radio == 1){
      nrow(data[data[,input$searchVar] <= as.numeric(input$searchVal),])
    }
    else if (input$radio == 2){
      nrow(data[data[,input$searchVar] == as.numeric(input$searchVal),])
    }
    else if (input$radio == 3){
      nrow(data[data[,input$searchVar] >= as.numeric(input$searchVal),])
    }
  }

# tableOutput("tabl2")
# output$tabl2 = function(){
#     if (input$radio == 1){
#       kable(DoTDF[DoTDF[,input$searchVar] <= as.numeric(input$searchVal),], "html") %>%
#         scroll_box(height = "500px", width = "910px")
#     }
#     else if (input$radio == 2){
#       kable(DoTDF[DoTDF[,input$searchVar] == as.numeric(input$searchVal),], "html") %>%
#         scroll_box(height = "500px", width = "910px")
#     }
#     else if (input$radio == 3){
#       kable(DoTDF[DoTDF[,input$searchVar] >= as.numeric(input$searchVal),], "html") %>%
#         scroll_box(height = "500px", width = "910px")
#     }
# }
```
</div>

### Predictions

<h4 style="text-align:center">Make a Prediction:</h4> 
<h5 style="text-align:center">Input values for the independent variables to get a predicted output.</h5>
<hr style="border-color: #ff6600;">

```{r echo = FALSE, warning = FALSE, fig.align = 'center'}

sidebarPanel(
  lapply(as.character(best_model_coef$variables), function(i) {
    textInput(inputId = i, label = paste(i, ":"), as.character(min(data[[i]])))}))

mainPanel(tags$div(align="center",
  tags$hr(),
  tags$h1(renderText("Predicted Price:")),
  tags$hr(),
  tags$h1(renderText({ 
    input_df = data.frame(matrix(ncol = 0, nrow = 1))
    for (i in as.character(best_model_coef$variables)){
      if ("factor" %in% class(data[[i]])){
        input_df[[i]] = as.character(input[[i]])}
      else {
        input_df[[i]] = as.numeric(input[[i]])
      }
    }
    scales::dollar(predict(best_model, input_df))
  })),
  tags$hr(style="border-color: #ff6600;"),
  renderPlotly({
    input_df = data.frame(matrix(ncol = 0, nrow = 1))
    for (i in as.character(best_model_coef$variables)){
      if ("factor" %in% class(data[[i]])){
        input_df[[i]] = as.character(input[[i]])}
      else {
        input_df[[i]] = as.numeric(input[[i]])
      }
    }
    Predicted_Price = predict(best_model, input_df)
    print(
      ggplotly(ggplot(data, aes(x = price)) +
                 geom_histogram(color = "steelblue", fill = "steelblue", alpha = .5, bins = 50) +
                 geom_vline(aes(xintercept = Predicted_Price), color = "#ff6600", linetype = "dashed", size = 1) +
                 scale_x_continuous("Price", labels = scales::dollar_format(), breaks = scales::pretty_breaks(n=10)) +
                 scale_y_continuous("Count") +
                 ggtitle("Diamond Price Density Curve") +
                 theme_minimal() +
                 theme(plot.title = element_text(color="#666666", face="bold", size=24)) +
                 theme(axis.title = element_text(color="#666666", face="bold", size=16, margin= margin(t=1, r=1, b=1, l=1))) +
                 theme(axis.text = element_text(color="#666666", size=10)) +
                 theme(plot.title = element_text(hjust = .5)) +
                 theme(axis.text.x = element_text(angle = 45, hjust = 1))
      ))})
  ))
```